---
title: "group_02_package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{group_02_package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CentralDogma)
```

### Decription of package 
The package includes 5 functions that creates the central dogma. From DNA to RNA (transcription) and from RNA to protein (translation). Finally the amino acid distribuition of the original DNA sequence is summarized in plot.  

### Function 1 description
The function, named random_DNA, generates a random DNA string of length N by sampling the 4 nucleotides A, G, T and C. 

### Function 2 description

This function takes as input a DNA sequence and generates its corresponding RNA sequence. It converges the nucleotide T (thymine) into U (uracil). The remaining nucleotides (A, C, and G) remain identical as these are also present in RNA sequences.
The input DNA sequence must not contain any characters other than the four nucleotides (A, C, G, and T), as well as be free from spaces or new lines.

### Function 3 description

This function is called extract codons. The input of the function is a character string that represents a sequence. The function divides the sequence into codons with the length of 3. 

### Function 4 description

This function is called decode_codons. The input of the function should be a vector of strings that each represent a codon, which is also the natural output of function 3.
The function uses the codon_table to translate the codons to amino acids and then returns a string representing the amino acids.

### Function 5 description

### Discussion of package 


